Ground state energy of quantum dots using the coupled cluster method

### 2018-04-12 project_2/article/article.tex
Add more theory on CC

% It's nice to be able to write your own name
\usepackage[T1]{fontenc}
% Automatic clickable links
\usepackage{hyperref}
% SI-units
\usepackage{siunitx}
% Enhanced math formatting
\usepackage{amsmath}
% Extended math symbols
\usepackage{amssymb}
% Include proof environment
\usepackage{amsthm}
\usepackage{enumerate}
% Import the tensor package for tensors
\usepackage{tensor}
% Include dod and dpd fracs
\usepackage{commath}
% Include font for the identity operator
\usepackage{dsfont}
% Include Tikz
\usepackage{tikz}
% Tikz add-on
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{positioning}
% Several figures in the same figure
\usepackage{subfig}
% Appendix
\usepackage[toc, page]{appendix}

@@

        \subsubsection{Energy of the coupled cluster approximation}
            When we're going to compute the energy of a system using the coupled
            cluster approximation we would ideally want to find the expectation
            value of the energy using the coupled cluster wavefunction.
            \begin{align}
                E = \bcc H\kcc.
            \end{align}
            As it turns out, this is an uncomfortable way of finding the energy
            as $T \neq T^{\dagger}$. Instead we will define what we call the
            \emph{similarity transformed Hamiltonian}. We plug the coupled
            cluster wavefunction into the Schrödinger equation.
            \begin{align}
                H\kcc = E\kcc.
            \end{align}
            Next, we left multiply with the inverse of the cluster expansion,
            i.e.,
            \begin{align}
                e^{-T}H\kcc = e^{-T}E\kcc
                = E \kslat.
            \end{align}
            Projecting this equation on the reference state we get
            \begin{align}
                E = \bslat e^{-T}H\kcc
                = \bslat e^{-T}He^{T}\kslat,
            \end{align}
            where in the latter inner-product we have located the similarity
            transformed Hamiltonian defined by
            \begin{align}
                \bar{H} \equiv e^{-T}He^{T}.
                \label{eq:similarity_transformed_hamiltonian}
            \end{align}

>>>>

% It's nice to be able to write your own name
\usepackage[T1]{fontenc}
% Automatic clickable links
\usepackage{hyperref}
% SI-units
\usepackage{siunitx}
% Enhanced math formatting
\usepackage{amsmath}
% Extended math symbols
\usepackage{amssymb}
% Include proof environment
\usepackage{amsthm}
\usepackage{enumerate}
% Import the tensor package for tensors
\usepackage{tensor}
% Include dod and dpd fracs
\usepackage{commath}
% Include font for the identity operator
\usepackage{dsfont}
% Include Tikz
\usepackage{tikz}
% Tikz add-on
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{positioning}
% Several figures in the same figure
\usepackage{subfig}
% Appendix
\usepackage[toc, page]{appendix}
\usepackage{simpler-wick}

@@

    \subsection{Energy of the coupled cluster approximation}
        When we're going to compute the energy of a system using the coupled
        cluster approximation we would ideally want to find the expectation
        value of the energy using the coupled cluster wavefunction.
        \begin{align}
            E = \bcc H\kcc.
        \end{align}
        As it turns out, this is an uncomfortable way of finding the energy
        as $T \neq T^{\dagger}$. Instead we will define what we call the
        \emph{similarity transformed Hamiltonian}. We plug the coupled
        cluster wavefunction into the Schrödinger equation.
        \begin{align}
            H\kcc = E\kcc.
        \end{align}
        Next, we left multiply with the inverse of the cluster expansion,
        i.e.,
        \begin{align}
            e^{-T}H\kcc = e^{-T}E\kcc
            = E \kslat.
        \end{align}
        Projecting this equation on the reference state we get
        \begin{align}
            E = \bslat e^{-T}H\kcc
            = \bslat e^{-T}He^{T}\kslat,
        \end{align}
        where in the latter inner-product we have located the similarity
        transformed Hamiltonian defined by
        \begin{align}
            \bar{H} \equiv e^{-T}He^{T}.
            \label{eq:similarity_transformed_hamiltonian}
        \end{align}

        \subsubsection{Normal ordered Hamiltonian}
            To get to the coupled cluster equations we need to write the
            Hamiltonian on a normal ordered form. We use Wick's theorem on the
            Fermi vacuum\footnote{Fermi vacuum corresponds to the reference
            Slater.}. The one-body part of the Hamiltonian thus becomes
            \begin{align}
                h &= \sum_{pq}h^p_q\acr{p}\ade{q}
                = \sum_{pq}h^p_q\para{
                    \{\acr{p}\ade{q}\}
                    + \{
                        \wick{\c a_{p}^{\dagger} \c a_{q}}
                    \}
                }
                \\
                &= h_N + \sum_{pq}\varepsilon_i.
            \end{align}
            The two-body part yields
            \begin{align}
                v &= \sum_{pqrs}w^{pq}_{rs}\acr{p}\acr{q}\ade{s}\ade{r}
            \end{align}
            % TODO: Fill in the remainder. Preferably in the appendix.
            We can then write the Hamiltonian in terms of the reference energy
            and the normal ordered Hamiltonian.
            \begin{align}
                H = H_N + \bslat H\kslat.
            \end{align}
            The energy equation thus becomes
            \begin{align}
                E &= \bslat\bar{H}\kslat
                = E_{\text{ref}} + \bslat e^{-T}H_N e^T\kslat.
            \end{align}

        By expanding the exponentials the similarity transformed Hamiltonian and
        recognizing the commutators we get the Baker-Campbell-Hausdorff
        expansion.
        \begin{align}
            \bar{H}
            &=
            H + \com{H}{T} + \half\com{\com{H}{T}}{T} + \dots.
        \end{align}
